Water Management

### 2020-02-22 Paper/paper.tex
unify citation style

% packages used for citations
\usepackage[
backend=bibtex,
style=alphabetic,
citestyle=authoryear,
natbib=true
]{biblatex}
\addbibresource{collection.bib}

@@

\subsubsection{Modification 3: Using Real Data for Rainfall}
Instead of simulating the rainfall with random numbers, we also use real data.
Comparing the results then allows us to draw conclusions on the accuracy of the simulation for that region. 
We use a dataset aquired from \cite{kaggle:2019}, that contains real rainfall data for the last 65 years in different regions of Bangladesh. % Zitation anpassen
% TODO describe how we fitted them to match the rainfall distribution

@@

where the weights $w_i$ are given as the solution to a linear system of equations and the nodes $x_i$ correspond to the zeros of the n-th Hermite polynomial. (\cite{seminar:week6})

@@

where $u(s,x)$ is the utility to gain from the control variable (action) $x$ in state $s$ %TODO: QUOTE Seminar Week 3.

@@

In systems theory, a system or a process is in a steady state, if the variables which define the behavior of the system are unchanging in time \cite{gagniuc2017markov}. 

>>>>

% packages used for citations
\usepackage[
backend=bibtex,
style=ieee,
citestyle=authoryear,
natbib=true
]{biblatex}
\addbibresource{collection.bib}

@@

\subsubsection{Modification 3: Using Real Data for Rainfall}
Instead of simulating the rainfall with random numbers, we also use real data.
Comparing the results then allows us to draw conclusions on the accuracy of the simulation for that region. 
We use a dataset aquired from \citep{kaggle:2019}, that contains real rainfall data for the last 65 years in different regions of Bangladesh. % Zitation anpassen
% TODO describe how we fitted them to match the rainfall distribution

@@

where the weights $w_i$ are given as the solution to a linear system of equations and the nodes $x_i$ correspond to the zeros of the n-th Hermite polynomial \citep{seminar:week6}.

@@

where $u(s,x)$ is the utility to gain from the control variable (action) $x$ in state $s$ \citep{seminar:week3}.

@@

In systems theory, a system or a process is in a steady state, if the variables which define the behavior of the system are unchanging in time \citep{gagniuc2017markov}. 
